---
title: "aarhus_exp_2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## data was saved in 
load("~/Desktop/copy_2020/social_individual_data_imported.RData")

## Importing data

we have four treatments. individual risk, individual ambiguity, social risk and social ambiguity.
question is whether situation and information that we have affects risk taking or not?

```{r}

#calculate ambiguity probabilities
#build cards
boxamb<-c(rep('a',14),rep('b',15),rep('c',10),rep('d',9),rep('e',7),rep('f',5))
#mix cards
boxamb1<-sample(boxamb,60)
boxamb2<-boxamb1
proboxamb<-array(NA,dim = c(100,50))
for (j in 1:100){
  boxamb1<-boxamb2
  for (i in 1:50){
    #count how many you have from a sample
    tmp<-sample(boxamb1,1)
    proboxamb[j,i]<-sum(boxamb1==tmp)/length(boxamb1)
    tmp2<-which(boxamb1==tmp)
    #remove that sample
    boxamb1<-boxamb1[-tmp2[1]]
  }
}
prob1<-colMeans(proboxamb)
prob2<-prob1*2
prob3<-prob1*3
prob4<-prob1*4
probamb<-data.frame('prob1'=prob1,'prob2'=prob2,'prob3'=prob3,'prob4'=prob4)

```

```{r}

#calculate risk probabilities
#build cards
boxrsk<-box<-c(rep('a',10),rep('b',10),rep('c',10),rep('d',10),rep('e',10),rep('f',10))
#mix cards
boxrsk1<-sample(boxrsk,60)
boxrsk2<-boxrsk1
proboxrsk<-array(NA,dim = c(100,50))
for (j in 1:100){
  boxrsk1<-boxrsk2
  for (i in 1:50){
    #count how many you have from a sample
    tmp<-sample(boxrsk1,1)
    proboxrsk[j,i]<-sum(boxrsk1==tmp)/length(boxrsk1)
    tmp2<-which(boxrsk1==tmp)
    #remove that sample
    boxrsk1<-boxrsk1[-tmp2[1]]
  }
}
prob1<-colMeans(proboxrsk)
prob2<-prob1*2
prob3<-prob1*3
prob4<-prob1*4
probrsk<-data.frame('prob1'=prob1,'prob2'=prob2,'prob3'=prob3,'prob4'=prob4)




```


```{r}
#Importing data
library("rjson")
#in windows
game_path_ind_amb <- "C:\\Users\\Arezoo\\Dropbox\\Experiment-Aarhus\\expaarhus201920\\individual\\ambiguity\\g*"
#in mac
game_path_ind_amb <- '/Users/au608780/Dropbox/Experiment-Aarhus/expaarhus201920/individual/ambiguity/g*'
game_name_ind_amb <- Sys.glob(game_path_ind_amb)
game_data_ind_amb <- lapply(game_name_ind_amb, function(x) fromJSON(file=x)) 
#in windows
participant_path_ind_amb <- "C:\\Users\\Arezoo\\Dropbox\\Experiment-Aarhus\\expaarhus201920\\individual\\ambiguity\\p*"
#in mac
participant_path_ind_amb <- '/Users/au608780/Dropbox/Experiment-Aarhus/expaarhus201920/individual/ambiguity/p*'
participant_name_ind_amb <- Sys.glob(participant_path_ind_amb)
participant_data_ind_amb <- lapply(participant_name_ind_amb, function(x) fromJSON(file=x)) 

#in windows
game_path_ind_rsk <- "C:\\Users\\Arezoo\\Dropbox\\Experiment-Aarhus\\expaarhus201920\\individual\\risky\\g*"
#in mac
game_path_ind_rsk <- '/Users/au608780/Dropbox/Experiment-Aarhus/expaarhus201920/individual/risky/g*'
game_name_ind_rsk <- Sys.glob(game_path_ind_rsk)
game_data_ind_rsk <- lapply(game_name_ind_rsk, function(x) fromJSON(file=x)) 
#in windows
participant_path_ind_rsk <- "C:\\Users\\Arezoo\\Dropbox\\Experiment-Aarhus\\expaarhus201920\\individual\\risky\\p*"
#in mac
participant_path_ind_rsk <- '/Users/au608780/Dropbox/Experiment-Aarhus/expaarhus201920/individual/risky/p*'

participant_name_ind_rsk <- Sys.glob(participant_path_ind_rsk)
participant_data_ind_rsk <- lapply(participant_name_ind_rsk, function(x) fromJSON(file=x)) 
# in windows
game_path_soc_amb <- "C:\\Users\\Arezoo\\Dropbox\\Experiment-Aarhus\\expaarhus201920\\social\\ambiguity\\g*"
#in mac
game_path_soc_amb <- '/Users/au608780/Dropbox/Experiment-Aarhus/expaarhus201920/social/ambiguity/g*'
game_name_soc_amb <- Sys.glob(game_path_soc_amb)
game_data_soc_amb <- lapply(game_name_soc_amb, function(x) fromJSON(file=x)) 
#in windows
participant_path_soc_amb <- "C:\\Users\\Arezoo\\Dropbox\\Experiment-Aarhus\\expaarhus201920\\social\\ambiguity\\p*"
#in mac
participant_path_soc_amb <- '/Users/au608780/Dropbox/Experiment-Aarhus/expaarhus201920/social/ambiguity/p*'

participant_name_soc_amb <- Sys.glob(participant_path_soc_amb)
participant_data_soc_amb <- lapply(participant_name_soc_amb, function(x) fromJSON(file=x)) 
#in windows
game_path_soc_rsk <- "C:\\Users\\Arezoo\\Dropbox\\Experiment-Aarhus\\expaarhus201920\\social\\risky\\g*"
# in mac
game_path_soc_rsk <- '/Users/au608780/Dropbox/Experiment-Aarhus/expaarhus201920/social/risky/g*'

game_name_soc_rsk <- Sys.glob(game_path_soc_rsk)
game_data_soc_rsk <- lapply(game_name_soc_rsk, function(x) fromJSON(file=x)) 
#in windows
participant_path_soc_rsk <- "C:\\Users\\Arezoo\\Dropbox\\Experiment-Aarhus\\expaarhus201920\\social\\risky\\p*"
#in mac
participant_path_soc_rsk <- '/Users/au608780/Dropbox/Experiment-Aarhus/expaarhus201920/social/risky/p*'

participant_name_soc_rsk <- Sys.glob(participant_path_soc_rsk)
participant_data_soc_rsk <- lapply(participant_name_soc_rsk, function(x) fromJSON(file=x)) 
# remove chracters from workspace
rm( list = ls()[ sapply( ls(), exists, mode="character")] )
```




```{r}
#import saved data
load("~/Desktop/copy_2020/social_individual_data_imported.RData")
# import dospert
library(tidyverse)
#dospert <- read.csv("~/Downloads/Domain-Specific Risk-Taking (Adult) Scale – Risk Taking_October 17, 2020_00.40.csv")
dospertnew <- dospert %>% select(18:48)
remove(dospert)
dospert <- dospertnew[-c(1,2), ]
names(dospert)[31] <- 'id'

for (i in 1:30){
  dospert[ ,i] <- as.numeric(dospert[ ,i])
}
for (j in 1:nrow(dospert)){
  dospert$ethical[j] <- dospert[j,6] + dospert[j,9] + dospert[j,10] + dospert[j,16] + dospert[j,29] + dospert[j,30]
  dospert$financial[j] <- dospert[j,12] + dospert[j,4] + dospert[j,18] + dospert[j,3] + dospert[j,14] + dospert[j,8]
  dospert$health[j] <- dospert[j,5] + dospert[j,15] + dospert[j,17] + dospert[j,20] + dospert[j,23] + dospert[j,26]
  dospert$recreational[j] <- dospert[j,2] + dospert[j,11] + dospert[j,13] + dospert[j,19] + dospert[j,24] + dospert[j,25]
  dospert$social[j] <- dospert[j,1] + dospert[j,7] + dospert[j,21] + dospert[j,22] + dospert[j,27] + dospert[j,28]
  dospert$gambling[j] <- dospert[j,3] + dospert[j,14] + dospert[j,8]
  dospert$investment[j] <- dospert[j,12] + dospert[j,4] + dospert[j,18]
}
dospert <- dospert %>% select(31:38)
dospert[30,1] <- "-rAZELrHF"
dospert[17,1] <- "-HU-qcYcd5"

```




## Counting Choice
# individual ambiguity choice counting
```{r}
##### individual ambiguity choice counting
dospert[which(dospert$id == participant_data_ind_amb[[1]][[2]][["id"]]), ] <- NA
participant_data_ind_amb[[1]][[2]] <- NULL #remove because of data loss
#remove from dospert

player_number_game_data_ind_amb <- NULL
tmprounddata <- NULL
ind_amb_choice <- array(NA, dim=c(length(participant_data_ind_amb),50,5))
ind_amb_score <- array(NA, dim=c(length(participant_data_ind_amb),50,5))
ind_amb_person <- array(NA, dim=c(length(participant_data_ind_amb),50,5))
participant_id_ind_amb <- array(NA, dim=c(length(participant_data_ind_amb),50,5)) 
rounddata <- NULL
testdata <- NULL
choice_number <- NULL

for (i in 1:length(participant_data_ind_amb))
{
  player_number_game_data_ind_amb[i] <- game_data_ind_amb[[i]][["maxPlayers"]]
}
#group of participants
for (i in 1:length(participant_data_ind_amb))# loop over group of participants play at the same time1
{ 
  for (j in 1:50) # loop over rounds
  {
    for (k in 1:5 ) #loop over number of participants in each test
    { 
      if ((k >player_number_game_data_ind_amb[i])) 
      {
        ind_amb_choice[i,j,k] <- NA
      }
      else{
        if (length(game_data_ind_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]]) != 0){
          
          ind_amb_choice[i,j,k]<-(length(game_data_ind_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["selectedColors"]]))
          
          
          ind_amb_score[i,j,k]<-(game_data_ind_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["result"]])
          
          participant_id_ind_amb[i,j,k]<-(game_data_ind_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["clientId"]])
          
          
        } 
      }
    }
  }
}
```


```{r}
######
#ind_amb
participant_number <-1
group_name <- 'ind_amb'
#ind_amb_choice[ind_amb_choice==1]<- 5
#ind_amb_choice[ind_amb_choice==4]<- 1
#ind_amb_choice[ind_amb_choice==5]<- 4
#ind_amb_choice[ind_amb_choice==2]<- 5
#ind_amb_choice[ind_amb_choice==3]<- 2
#ind_amb_choice[ind_amb_choice==5]<- 3
tmplist <- list()
tmprow <- list()
trial_max<- NA
trial_min<- NA
trial_mean<- NA
for (i in 1:length(participant_data_ind_amb)){
  datalist <- list()
  rowdata <- list()
  for (k in 1:player_number_game_data_ind_amb[i]) # participants
  {
    personclk <- array(0,50)
    round_number <- 1:50
    trialscore<-ind_amb_score[i,round_number,k]
    personclk <- ind_amb_person[i,round_number,k]
    risk <- ind_amb_choice[i,round_number,k]
    probab<-array(NA,50)
    for (z1 in 1:length(risk)){
      if (!is.na(risk[z1])){
    if (risk[z1] == 4){
      probab[z1]<-probamb$prob4[z1]
    }else if (risk[z1] == 3){
      probab[z1]<-probamb$prob3[z1]
    }else if (risk[z1] == 2){
      probab[z1]<-probamb$prob2[z1]
    }else if (risk[z1] == 1){
      probab[z1]<-probamb$prob1[z1]
    }
      }
    }
    id <- participant_id_ind_amb[i,round_number,k]
    idclk <- NA
    d <- (data.frame('participant_number'= participant_number,'id'=id,'group_name'= group_name,'round_number'= round_number,'risk'=risk,'probability'=probab,'round_score'=trialscore,'person_click'= personclk,'id_click'=idclk,'data_gathering_group'=i,'data_gathering_participant_id'= k,'other_max_score'=trial_max,'other_min_score'=trial_min,'other_mean_score'=trial_mean))
r<-data.frame('id'=id[1],'group_name'= group_name,'risk'=mean(risk,na.rm=TRUE),'round_score'=mean(trialscore,na.rm=TRUE),'person_click'= mean(personclk,na.rm=TRUE),'other_max_score'=trial_max,'other_min_score'=trial_min,'other_mean_score'=trial_mean)

    datalist[[k]] <- d
    rowdata[[k]]<- r
    participant_number <- participant_number + 1
  }
  tmplist[[i]] <- dplyr::bind_rows(datalist)
  tmprow[[i]] <- dplyr::bind_rows(rowdata)
}
big_ind_amb <- dplyr::bind_rows(tmplist)
big_ind_amb_row <- dplyr::bind_rows(tmprow)
#big_ind_amb$person_click[round_number == 50] <- 0
#big_person <-  dplyr::bind_rows(big_person_ind_amb,big_person_ind_amb)
#####
ind_amb_gender<-NA
ind_amb_age <-NA
ind_amb_id<-NA
z<-1
for (i in 1:length(participant_data_ind_amb)){
  for (j in 1:length(participant_data_ind_amb[[i]])){
    ind_amb_gender[z]<-(participant_data_ind_amb[[i]][[j]][["gender"]])
    ind_amb_age[z]<-(participant_data_ind_amb[[i]][[j]][["age"]])
    ind_amb_id[z]<-(participant_data_ind_amb[[i]][[j]][["id"]])
    z<-z+1
  }
}
ind_amb_age_gender<-data.frame('id'=ind_amb_id,'gender'=ind_amb_gender,'age'=ind_amb_age)
big_ind_amb <- merge(unique(big_ind_amb),(ind_amb_age_gender),by="id",all = TRUE)
big_ind_amb_row <- merge(unique(big_ind_amb_row),(ind_amb_age_gender),by="id",all = TRUE)

big_ind_amb<-big_ind_amb[-which(is.na(big_ind_amb$risk)),]
#big_ind_amb_row<-big_ind_amb_row[-which(is.na(big_ind_amb_row$risk)),]

```


# individual risky choice counting
```{r}
##### individual risky choice counting

#dospert[which(dospert$id == participant_data_ind_rsk[[9]][[2]][["id"]]), ] <- NA


##### this person's data is not complete _EWdQ-qcy
tmp <- participant_data_ind_rsk[[3]][[1]]
participant_data_ind_rsk[[3]][[1]] <- participant_data_ind_rsk[[3]][[2]]
participant_data_ind_rsk[[3]][[2]] <- tmp
dospert[which(dospert$id == participant_data_ind_rsk[[3]][[1]][["id"]]), ] <- NA
participant_data_ind_rsk[[3]][[1]] <- NULL
game_data_ind_rsk[[3]][["maxPlayers"]] <-2 
#####
participant_data_ind_rsk[[13]] <- NULL #data loss
game_data_ind_rsk[[13]] <- NULL #data loss

participant_data_ind_rsk[[5]][[3]] <- NULL
game_data_ind_rsk[[5]][["maxPlayers"]] <-2 
dospert[which(dospert$id == participant_data_ind_rsk[[9]][[2]][["id"]]), ] <- NA
participant_data_ind_rsk[[9]][[2]] <- NULL
game_data_ind_rsk[[9]][["maxPlayers"]] <- game_data_ind_rsk[[9]][["maxPlayers"]] -1

player_number_game_data_ind_rsk <- NULL
tmprounddata <- NULL
ind_rsk_choice <- array(NA, dim=c(length(participant_data_ind_rsk),50,5))
ind_rsk_score <- array(NA, dim=c(length(participant_data_ind_rsk),50,5))
ind_rsk_person <- array(NA, dim=c(length(participant_data_ind_rsk),50,5))
participant_id_ind_rsk <- array(NA, dim=c(length(participant_data_ind_rsk),50,5)) 
rounddata <- NULL
testdata <- NULL
choice_number <- NULL

for (i in 1:length(participant_data_ind_rsk))
{
  player_number_game_data_ind_rsk[i] <- game_data_ind_rsk[[i]][["maxPlayers"]]
}
#group of participants
for (i in 1:length(participant_data_ind_rsk))# loop over group of participants play at the same time1
{ 
  for (j in 1:50) # loop over rounds
  {
    for (k in 1:5 ) #loop over number of participants in each test
    { 
      if ((k >player_number_game_data_ind_rsk[i])) 
      {
        ind_rsk_choice[i,j,k] <- NA
      }
      else{
        if (length(game_data_ind_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]]) != 0){
      
      ind_rsk_choice[i,j,k]<-(length(game_data_ind_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["selectedColors"]]))
      
      
      ind_rsk_score[i,j,k]<-(game_data_ind_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["result"]])
      
      participant_id_ind_rsk[i,j,k]<-(game_data_ind_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["clientId"]])
      
     
        } 
    }
  }
  }
}
######
#ind_rsk
participant_number <-1
group_name <- 'ind_rsk'

#ind_rsk_choice[ind_rsk_choice==1]<- 5
#ind_rsk_choice[ind_rsk_choice==4]<- 1
#ind_rsk_choice[ind_rsk_choice==5]<- 4
#ind_rsk_choice[ind_rsk_choice==2]<- 5
#ind_rsk_choice[ind_rsk_choice==3]<- 2
#ind_rsk_choice[ind_rsk_choice==5]<- 3

tmplist <- list()
tmprow <- list()
trial_max<- NA
trial_min<- NA
trial_mean<- NA
for (i in 1:length(participant_data_ind_rsk)){
  datalist <- list()
  rowdata <- list()
  for (k in 1:player_number_game_data_ind_rsk[i]) # participants
  {
    personclk <- array(0,50)
    round_number <- 1:50
    trialscore<-ind_rsk_score[i,round_number,k]
    personclk <- ind_rsk_person[i,round_number,k]
    risk <- ind_rsk_choice[i,round_number,k]
       probab<-array(NA,50)
    for (z1 in 1:length(risk)){
      if (!is.na(risk[z1])){
    if (risk[z1] == 4){
      probab[z1]<-probrsk$prob4[z1]
    }else if (risk[z1] == 3){
      probab[z1]<-probrsk$prob3[z1]
    }else if (risk[z1] == 2){
      probab[z1]<-probrsk$prob2[z1]
    }else if (risk[z1] == 1){
      probab[z1]<-probrsk$prob1[z1]
    }
      }
    }
    id <- participant_id_ind_rsk[i,round_number,k]
   idclk <- NA
   r<-data.frame('id'=id[1],'group_name'= group_name,'risk'=mean(risk,na.rm=TRUE),'round_score'=mean(trialscore,na.rm=TRUE),'person_click'= mean(personclk,na.rm=TRUE),'other_max_score'=trial_max,'other_min_score'=trial_min,'other_mean_score'=trial_mean)
    d <- (data.frame('participant_number'= participant_number,'id'=id,'group_name'= group_name,'round_number'= round_number,'risk'=risk,'probability'=probab,'round_score'=trialscore,'person_click'= personclk,'id_click'=idclk,'data_gathering_group'=i,'data_gathering_participant_id'= k,'other_max_score'=trial_max,'other_min_score'=trial_min,'other_mean_score'=trial_mean))
    datalist[[k]] <- d
    rowdata[[k]]<- r
    participant_number <- participant_number + 1
  }
  tmplist[[i]] <- dplyr::bind_rows(datalist)
  tmprow[[i]] <- dplyr::bind_rows(rowdata)
}
big_ind_rsk <- dplyr::bind_rows(tmplist)
big_ind_rsk_row <- dplyr::bind_rows(tmprow)
#big_ind_rsk$person_click[round_number == 50] <- 0
#big_person <-  dplyr::bind_rows(big_person_ind_rsk,big_person_ind_rsk)
#####
ind_rsk_gender<-NA
ind_rsk_age <-NA
ind_rsk_id<-NA
z<-1
for (i in 1:length(participant_data_ind_rsk)){
  for (j in 1:length(participant_data_ind_rsk[[i]])){
    ind_rsk_gender[z]<-(participant_data_ind_rsk[[i]][[j]][["gender"]])
    ind_rsk_age[z]<-(participant_data_ind_rsk[[i]][[j]][["age"]])
    ind_rsk_id[z]<-(participant_data_ind_rsk[[i]][[j]][["id"]])
    z<-z+1
  }
}
ind_rsk_age_gender<-data.frame('id'=ind_rsk_id,'gender'=ind_rsk_gender,'age'=ind_rsk_age)
big_ind_rsk <- merge(unique(big_ind_rsk),(ind_rsk_age_gender),by="id",all = TRUE)
big_ind_rsk_row <- merge(unique(big_ind_rsk_row),(ind_rsk_age_gender),by="id",all = TRUE)
big_ind_rsk_row<-big_ind_rsk_row[-which(is.na(big_ind_rsk_row$risk)),]
big_ind_rsk<-big_ind_rsk[-which(is.na(big_ind_rsk$risk)),]
```


# social ambiguity choice counting
```{r}
##### social ambiguity choice counting

player_number_game_data_soc_amb <- NULL
tmprounddata <- NULL
soc_amb_choice <- array(NA, dim=c(5,50,5))
soc_amb_score <- array(NA, dim=c(5,50,5))
soc_amb_person <- array(NA, dim=c(5,50,5))
soc_amb_id_person <- array(NA, dim=c(5,50,5))
participant_id_soc_amb <- array(NA, dim=c(5,50,5)) 
rounddata <- NULL
testdata <- NULL
choice_number <- NULL

for (i in 1:length(participant_data_soc_amb))
{
  player_number_game_data_soc_amb[i] <- game_data_soc_amb[[i]][["maxPlayers"]]
}
#group of participants
for (i in 1:length(participant_data_soc_amb))# loop over group of participants play at the same time1
{ 
  for (j in 1:50) # loop over rounds
  {
    for (k in 1:5 ) #loop over number of participants in each test
    { 
      soc_amb_choice[i,j,k]<-(length(game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["selectedColors"]]))
      
      
      soc_amb_score[i,j,k]<-(game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["result"]])
      
      participant_id_soc_amb[i,j,k]<-(game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["clientId"]])
      if (j !=50){
      if (length(game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["socialSceneData"]][[1]][["selectedParticipantId"]]) != 0 ){
        soc_amb_person[i,j,k]<-(length(game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["socialSceneData"]][[1]][["selectedParticipantId"]]))
        #  soc_amb_other_scores[i,j,k]
        soc_amb_id_person[i,j,k]<-paste((game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["socialSceneData"]][[1]][["selectedParticipantId"]]),collapse=",")
      }
      }
      
    }
  }
}

# find average & max scores of the other participants in each round
trial_mean_soc_amb <- array(NA,c(5,50,5))
trial_max_soc_amb <- array(NA,c(5,50,5))
trial_min_soc_amb <- array(NA,c(5,50,5))
nxt_risk_soc_amb <- array(NA,c(5,50,5))

#soc_amb_choice[soc_amb_choice==1]<- 5
#soc_amb_choice[soc_amb_choice==4]<- 1
#soc_amb_choice[soc_amb_choice==5]<- 4
#soc_amb_choice[soc_amb_choice==2]<- 5
#soc_amb_choice[soc_amb_choice==3]<- 2
#soc_amb_choice[soc_amb_choice==5]<- 3


for (i in 1:length(participant_data_soc_amb)){ #on groups
  datalist <- list()
  
  for (j in 1:max(round_number)) {
    tmparr <- 0
    for (k in 1:5)
      # on participants
    {
      tmparr <- soc_amb_score[i,j,]
      trial_mean_soc_amb[i,j,k] <- mean(tmparr[! tmparr %in% soc_amb_score[i,j,k] | duplicated (tmparr)])
      trial_max_soc_amb[i,j,k] <- max(tmparr[! tmparr %in% soc_amb_score[i,j,k] | duplicated (tmparr)])
      trial_min_soc_amb[i,j,k] <- min(tmparr[! tmparr %in% soc_amb_score[i,j,k] | duplicated (tmparr)])
      if(j !=50){
        nxt_risk_soc_amb[i,j,k] <- soc_amb_choice[i,j+1,k]
      }
      else
        nxt_risk_soc_amb[i,j,k] <- NA
    }
  }
}


#soc_amb
participant_number <-1
group_name <- 'soc_amb'
tmplist <- list()
tmprow <- list()
trial_max <- array(NA,c(5,50,5))
trial_min <- array(NA,c(5,50,5))
trial_mean <- array(NA,c(5,50,5))
for (i in 1:length(participant_data_soc_amb)){
  datalist <- list()
  rowdata <- list()
  for (k in 1:player_number_game_data_soc_amb[i]) # participants
  {
    personclk <- array(0,50)
    round_number <- 1:50
    trial_max<- trial_max_soc_amb[i,round_number,k]
    trial_min<- trial_min_soc_amb[i,round_number,k]
    trial_mean<- trial_mean_soc_amb[i,round_number,k]
    trialscore<-soc_amb_score[i,round_number,k]
    personclk <- soc_amb_person[i,round_number,k]
    idclk <- soc_amb_id_person[i,round_number,k]
    risk <- soc_amb_choice[i,round_number,k]
       probab<-array(NA,50)
    for (z1 in 1:length(risk)){
      if (!is.na(risk[z1])){
    if (risk[z1] == 4){
      probab[z1]<-probamb$prob4[z1]
    }else if (risk[z1] == 3){
      probab[z1]<-probamb$prob3[z1]
    }else if (risk[z1] == 2){
      probab[z1]<-probamb$prob2[z1]
    }else if (risk[z1] == 1){
      probab[z1]<-probamb$prob1[z1]
    }
      }
    }
    id <- participant_id_soc_amb[i,round_number,k]
    d <- (data.frame('participant_number'= participant_number,'id'=id,'group_name'= group_name,'round_number'= round_number,'risk'=risk,'probability'=probab,'round_score'=trialscore,'person_click'= personclk,'id_click'=idclk,'data_gathering_group'=i,'data_gathering_participant_id'= k,'other_max_score'=trial_max,'other_min_score'=trial_min,'other_mean_score'=trial_mean))
    r<-data.frame('id'=id[1],'group_name'= group_name,'risk'=mean(risk,na.rm=TRUE),'round_score'=mean(trialscore,na.rm=TRUE),'person_click'= mean(personclk,na.rm=TRUE),'other_max_score'=mean(trial_max,na.rm=TRUE),'other_min_score'=mean(trial_min,na.rm=TRUE),'other_mean_score'=mean(trial_mean,na.rm=TRUE))

    datalist[[k]] <- d
    rowdata[[k]]<- r
    participant_number <- participant_number + 1
  }
  tmplist[[i]] <- dplyr::bind_rows(datalist)
  tmprow[[i]] <- dplyr::bind_rows(rowdata)
}
big_soc_amb <- dplyr::bind_rows(tmplist)
big_soc_amb_row <- dplyr::bind_rows(tmprow)
#big_soc_amb$person_click[round_number == 50] <- 0
#big_person <-  dplyr::bind_rows(big_person_soc_amb,big_person_soc_amb)
#####
soc_amb_gender<-NA
soc_amb_age <-NA
soc_amb_id<-NA
z<-1
for (i in 1:length(participant_data_soc_amb)){
  for (j in 1:length(participant_data_soc_amb[[i]])){
    soc_amb_gender[z]<-(participant_data_soc_amb[[i]][[j]][["gender"]])
    soc_amb_age[z]<-(participant_data_soc_amb[[i]][[j]][["age"]])
    soc_amb_id[z]<-(participant_data_soc_amb[[i]][[j]][["id"]])
    z<-z+1
  }
}
soc_amb_age_gender<-data.frame('id'=soc_amb_id,'gender'=soc_amb_gender,'age'=soc_amb_age)
big_soc_amb <- merge(unique(big_soc_amb),(soc_amb_age_gender),by="id",all = TRUE)
big_soc_amb_row <- merge(unique(big_soc_amb_row),(soc_amb_age_gender),by="id",all = TRUE)
#big_soc_amb<-big_soc_amb[-which(is.na(big_soc_amb$risk)),]
#big_soc_amb_row<-big_soc_amb_row[-which(is.na(big_soc_amb_row$risk)),]



```

# social risky choice counting
```{r}
##### social risky choice counting
player_number_game_data_soc_rsk <- NULL
tmprounddata <- NULL
soc_rsk_choice <- array(NA, dim=c(5,50,5))
soc_rsk_score <- array(NA, dim=c(5,50,5))
soc_rsk_person <- array(NA, dim=c(5,50,5))
soc_rsk_id_person <- array(NA, dim=c(5,50,5))
participant_id_soc_rsk <- array(NA, dim=c(5,50,5)) 
rounddata <- NULL
testdata <- NULL
choice_number <- NULL

for (i in 1:length(participant_data_soc_rsk))
{
  player_number_game_data_soc_rsk[i] <- game_data_soc_rsk[[i]][["maxPlayers"]]
}
#group of participants
for (i in 1:length(participant_data_soc_rsk))# loop over group of participants play at the same time1
{ 
  for (j in 1:50) # loop over rounds
  {
    for (k in 1:5 ) #loop over number of participants in each test
    { 
      soc_rsk_choice[i,j,k]<-(length(game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["selectedColors"]]))
      
      
      soc_rsk_score[i,j,k]<-(game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["result"]])
      
      participant_id_soc_rsk[i,j,k]<-(game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["clientId"]])
      if (j !=50){
      if (length(game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["socialSceneData"]][[1]][["selectedParticipantId"]]) != 0 ){
        soc_rsk_person[i,j,k]<-(length(game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["socialSceneData"]][[1]][["selectedParticipantId"]]))
        #  soc_rsk_other_scores[i,j,k]
        soc_rsk_id_person[i,j,k]<-paste((game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["socialSceneData"]][[1]][["selectedParticipantId"]]),collapse=",")
      }
      }
      
    }
  }
}



trial_mean_soc_rsk <- array(NA,c(5,50,5))
trial_max_soc_rsk <- array(NA,c(5,50,5))
trial_min_soc_rsk <- array(NA,c(5,50,5))
nxt_risk_soc_rsk <- array(NA,c(5,50,5))

#soc_rsk_choice[soc_rsk_choice==1]<- 5
#soc_rsk_choice[soc_rsk_choice==4]<- 1
#soc_rsk_choice[soc_rsk_choice==5]<- 4
#soc_rsk_choice[soc_rsk_choice==2]<- 5
#soc_rsk_choice[soc_rsk_choice==3]<- 2
#soc_rsk_choice[soc_rsk_choice==5]<- 3


for (i in 1:length(participant_data_soc_rsk)){ #on groups
  datalist <- list()
  
  for (j in 1:max(round_number)) {
    tmparr <- 0
    for (k in 1:5)
      # on participants
    {
      tmparr <- soc_rsk_score[i,j,]
      trial_mean_soc_rsk[i,j,k] <- mean(tmparr[! tmparr %in% soc_rsk_score[i,j,k] | duplicated (tmparr)])
      trial_max_soc_rsk[i,j,k] <- max(tmparr[! tmparr %in% soc_rsk_score[i,j,k] | duplicated (tmparr)])
      trial_min_soc_rsk[i,j,k] <- min(tmparr[! tmparr %in% soc_rsk_score[i,j,k] | duplicated (tmparr)])
      if(j !=50){
        nxt_risk_soc_rsk[i,j,k] <- soc_rsk_choice[i,j+1,k]
      }
      else
        nxt_risk_soc_rsk[i,j,k] <- NA
    }
  }
}


#soc_rsk
participant_number <-1
group_name <- 'soc_rsk'
tmplist <- list()
tmprow <- list()
trial_max <- array(NA,c(5,50,5))
trial_min <- array(NA,c(5,50,5))
trial_mean <- array(NA,c(5,50,5))
for (i in 1:length(participant_data_soc_rsk)){
  datalist <- list()
  rowdata <- list()
  for (k in 1:player_number_game_data_soc_rsk[i]) # participants
  {
    personclk <- array(0,50)
    round_number <- 1:50
    trial_max<- trial_max_soc_rsk[i,round_number,k]
    trial_min<- trial_min_soc_rsk[i,round_number,k]
    trial_mean<- trial_mean_soc_rsk[i,round_number,k]
    trialscore<-soc_rsk_score[i,round_number,k]
    personclk <- soc_rsk_person[i,round_number,k]
    idclk <- soc_rsk_id_person[i,round_number,k]
    risk <- soc_rsk_choice[i,round_number,k]
       probab<-array(NA,50)
    for (z1 in 1:length(risk)){
      if (!is.na(risk[z1])){
    if (risk[z1] == 4){
      probab[z1]<-probrsk$prob4[z1]
    }else if (risk[z1] == 3){
      probab[z1]<-probrsk$prob3[z1]
    }else if (risk[z1] == 2){
      probab[z1]<-probrsk$prob2[z1]
    }else if (risk[z1] == 1){
      probab[z1]<-probrsk$prob1[z1]
    }
      }
    }
    id <- participant_id_soc_rsk[i,round_number,k]
    d <- (data.frame('participant_number'= participant_number,'id'=id,'group_name'= group_name,'round_number'= round_number,'risk'=risk,'probability'=probab,'round_score'=trialscore,'person_click'= personclk,'id_click'=idclk,'data_gathering_group'=i,'data_gathering_participant_id'= k,'other_max_score'=trial_max,'other_min_score'=trial_min,'other_mean_score'=trial_mean))
    r<-data.frame('id'=id[1],'group_name'= group_name,'risk'=mean(risk,na.rm=TRUE),'round_score'=mean(trialscore,na.rm=TRUE),'person_click'= mean(personclk,na.rm=TRUE),'other_max_score'=mean(trial_max,na.rm=TRUE),'other_min_score'=mean(trial_min,na.rm=TRUE),'other_mean_score'=mean(trial_mean,na.rm=TRUE))

    datalist[[k]] <- d
    rowdata[[k]]<- r
    participant_number <- participant_number + 1
  }
  tmplist[[i]] <- dplyr::bind_rows(datalist)
  tmprow[[i]] <- dplyr::bind_rows(rowdata)
}
big_soc_rsk <- dplyr::bind_rows(tmplist)
big_soc_rsk_row <- dplyr::bind_rows(tmprow)
#big_soc_rsk$person_click[round_number == 50] <- 0
#big_person <-  dplyr::bind_rows(big_person_soc_rsk,big_person_soc_rsk)
#####
soc_rsk_gender<-NA
soc_rsk_age <-NA
soc_rsk_id<-NA
z<-1
for (i in 1:length(participant_data_soc_rsk)){
  for (j in 1:length(participant_data_soc_rsk[[i]])){
    soc_rsk_gender[z]<-(participant_data_soc_rsk[[i]][[j]][["gender"]])
    soc_rsk_age[z]<-(participant_data_soc_rsk[[i]][[j]][["age"]])
    soc_rsk_id[z]<-(participant_data_soc_rsk[[i]][[j]][["id"]])
    z<-z+1
  }
}
soc_rsk_age_gender<-data.frame('id'=soc_rsk_id,'gender'=soc_rsk_gender,'age'=soc_rsk_age)
big_soc_rsk <- merge(unique(big_soc_rsk),(soc_rsk_age_gender),by="id",all = TRUE)
big_soc_rsk_row <- merge(unique(big_soc_rsk_row),(soc_rsk_age_gender),by="id",all = TRUE)



```

```{r}
#ask if its correct?
# to make all the same size, select size of the lowest one 
#big_data <- dplyr::bind_rows(big_ind_rsk[1:1000, ],big_ind_amb[1:1000, ],big_soc_rsk[1:1000, ],big_soc_amb[1:1000, ])
###make dataframe of all
big_data <- dplyr::bind_rows(big_ind_rsk,big_ind_amb,big_soc_rsk,big_soc_amb)
big_data_row <- dplyr::bind_rows(big_ind_rsk_row,big_ind_amb_row,big_soc_rsk_row,big_soc_amb_row)
big_data$gender[big_data$gender=='Female'| big_data$gender=='F' |big_data$gender=='female'| big_data$gender=='FEMALE'| big_data$gender=='Woman']<-'f'
big_data$gender[big_data$gender=='Male'| big_data$gender=='M' |big_data$gender=='male'|big_data$gender=='MALE']<-'m'

big_data_row$gender[big_data_row$gender=='Female'| big_data_row$gender=='F' |big_data_row$gender=='female'| big_data_row$gender=='FEMALE'| big_data_row$gender=='Woman']<-'f'
big_data_row$gender[big_data_row$gender=='Male'| big_data_row$gender=='M' |big_data_row$gender=='male'|big_data_row$gender=='MALE']<-'m'
big_data_row <- merge(unique(big_data_row),(dospert),by="id",all = TRUE)
big_data_row$dospert <- big_data_row$ethical + big_data_row$financial + big_data_row$health+big_data_row$recreational+big_data_row$social
big_data_row<- big_data_row[-which(is.na(big_data_row$risk)),]
  big_data_avg<-data.frame('id'=big_data_row$id,'gender'=big_data_row$gender,'age'=big_data_row$age,'group_name'=big_data_row$group_name,'risk_avg'=scale(big_data_row$risk),'score_avg'=big_data_row$round_score,'click_avg'=scale(big_data_row$person_click),'other_max_avg'=scale(big_data_row$other_max_score),'other_min_avg'=scale(big_data_row$other_min_score),'other_mean_avg'=scale(big_data_row$other_mean_score),'dospert'=scale(big_data_row$dospert),'financial'=scale(big_data_row$financial))
  
   big_data_avg$group_name2<-big_data_avg$group_name
big_data_avg$group_name2[big_data_avg$group_name2=='ind_rsk'|big_data_avg$group_name2=='soc_rsk']<-'rsk'
big_data_avg$group_name2[big_data_avg$group_name2=='ind_amb'|big_data_avg$group_name2=='soc_amb']<-'amb'

 big_data_avg$group_name3<-big_data_avg$group_name
big_data_avg$group_name3[big_data_avg$group_name3=='soc_rsk'|big_data_avg$group_name3=='soc_amb']<-'soc'
big_data_avg$group_name3[big_data_avg$group_name3=='ind_amb'|big_data_avg$group_name3=='ind_rsk']<-'ind'
  
#####
```

```{r}
#plots in averaging data
library(stargazer)
library(lme4)
(split_plot <- ggplot(aes(big_data_avg$financial, risk_avg), data = big_data_avg) + 
  geom_point() + 
  facet_wrap(~ group_name) + # create a facet for each mountain range
  xlab("score_average") + 
  ylab("risk_average"))
#model in average data
smodel<-lm(risk_avg~group_name,data = big_data_avg)
 summary(smodel)
 
  stargazer(smodel, type = "text",
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")
  
  smodel2<-lmer(risk_avg~group_name2+(1|financial)+(1|gender)+(1|age)+(1|score_avg)+(1|other_max_avg)+(1|other_mean_avg),data = big_data_avg)
  summary(smodel2)
```

```{r}
big_data <- merge(unique(big_data),(dospert),by="id",all = TRUE)
#big_data$dospert <- big_data$ethical + big_data$financial + big_data$health+big_data$recreational+big_data$social
big_data<- big_data[-which(is.na(big_data$risk)),]
```
## Analysis part new

```{r}

 big_data$zrisk<-scale(big_data$risk)
 big_data$zround_score<-scale(big_data$round_score)
 big_data$zother_max_score<-scale(big_data$other_max_score)
 big_data$zother_mean_score<-scale(big_data$other_mean_score)
 big_data$zother_min_score<-scale(big_data$other_min_score)
 big_data$zage<-scale(as.numeric(big_data$age))
 big_data$zfinancial<-scale(big_data$financial)
 #big_data$zdospert<-scale(big_data$dospert)
 #big_data<-big_data[-which(is.na(big_data$risk)),]
 
 big_data$group_name2<-big_data$group_name
big_data$group_name2[big_data$group_name2=='ind_rsk'|big_data$group_name2=='soc_rsk']<-'rsk'
big_data$group_name2[big_data$group_name2=='ind_amb'|big_data$group_name2=='soc_amb']<-'amb'

 big_data$group_name3<-big_data$group_name
big_data$group_name3[big_data$group_name3=='soc_rsk'|big_data$group_name3=='soc_amb']<-'soc'
big_data$group_name3[big_data$group_name3=='ind_amb'|big_data$group_name3=='ind_rsk']<-'ind'
 #checked

# Do some plots

(split_plot <- ggplot(aes(big_data$zround_score, zrisk), data = big_data) + 
  geom_point() + 
  facet_wrap(~ group_name) + # create a facet for each mountain range
  xlab("round score") + 
  ylab("risk"))
```
#analysis new
```{r}
library(ggplot2)
library(sjPlot)
library(lme4)
variable_names <- list(
  "ind_amb" = "Individual Ambiguity" ,
  "ind_rsk" = "Individual Risk" ,
  "soc_amb" = "Social Ambiguity" ,
  "soc_rsk" = "Social Risk"
  )

#names(soc.labs) <- c("Social", "Individual")
#names(rsk.labs) <- c("Risk", "Ambiguity")
variable_labeller <- function(variable,value){
  return(variable_names[value])
}

big_data$group_name2[big_data$group_name2=='rsk']='Risk'
 big_data$group_name2[big_data$group_name2=='amb']='Ambiguity'
 big_data$group_name3[big_data$group_name3=='ind']='Individual'
 big_data$group_name3[big_data$group_name3=='soc']='Social'

ggplot((big_data), aes(x= risk,  group=group_name)) + 
    geom_bar(aes(y = ..prop..), stat="count") +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -.6, size=2) +
    labs(y = "Percentage", fill='risk') +
    #facet_grid(group_name2~group_name3,labeller=variable_labeller) +
  facet_grid(group_name2~group_name3) +
    scale_y_continuous(labels = scales::percent)+theme_minimal()

#hypothesis 1: more risky choice in risk group than ambiguity
#group name 2 categorized risk and ambiguity
model_rsk_vs_amb<-lmer(zrisk~group_name2+(1|id),data = big_data)
 summary(model_rsk_vs_amb)
tab_model(model_rsk_vs_amb)
 #both groups have significant effect on risk-taking
 model_soc_vs_ind<-lmer(zrisk~group_name3+(1|id),data = big_data)
 summary(model_soc_vs_ind)
tab_model(model_soc_vs_ind)


 #calculate the effect size
 r2.corr.mer <- function(m) {
    lmfit <-  lm(model.response(model.frame(m)) ~ fitted(m))
    summary(lmfit)$r.squared
 }
 #r2.corr.mer(model4r)
wilcox.test(big_data$zrisk[big_data$group_name=='soc_rsk'|big_data$group_name=='ind_rsk'],big_data$zrisk[big_data$group_name=='soc_amb'|big_data$group_name=='ind_amb'],alternative = 'less')
#tab_model(model3r)
# so hypo 1 is not true and ambiguity take more risk

```
```{r}
#hypothesis 2: more risky choice in social group than individual
#group name 3 categorized social and individual groups
model1s<-lm(zrisk~group_name3,data = big_data)
 summary(model1s)
 wilcox.test(big_data$zrisk[big_data$group_name3=='soc'],big_data$zrisk[big_data$group_name3=='ind'],alternative = 'greater')
# so hypo 2 is true and social take more risk

```



```{r}
#models
model1<- lm(zrisk~group_name,data = big_data)
model1<- lm(zrisk~group_name+zround_score+zother_max_score+zother_min_score+zother_mean_score,data = big_data)
rs ~ gp + (1|id) + (1|rsc) + (1|fn) + (1|gn)
model1<-lmer(zrisk~group_name+(1|id)+(1|gender)+(1|zage)+zround_score+(1|zdospert)+zother_max_score+zother_min_score+zother_mean_score,data = big_data)
summary(model1)

(prelim_plot <- ggplot(big_data, aes(x = group_name, y = zrisk)) +
  geom_point() +
  geom_smooth(method = "lm"))
```


```{r}
test <- wilcox.test(big_data$financial[big_data$group_name == 'soc_rsk'],big_data$financial[big_data$group_name == 'soc_amb'])
N <- length(big_data$financial[big_data$group_name == 'soc_rsk'])
  test$p.value
  Zstat<-qnorm(test$p.value)
  Zstat
  r <- abs(Zstat)/sqrt(N)
  r
  c(Zstat,test$p.value,r)
  median((big_data$risk[big_data$group_name == 'soc_rsk' | big_data$group_name == 'ind_rsk']),na.rm = TRUE)
   median((big_data$risk[big_data$group_name == 'soc_amb' | big_data$group_name == 'ind_amb']),na.rm = TRUE)


```

## Analysis part 
#risk_taking
```{r}
##### risk all vs ambiguity all
N <- length(big_data$risk[big_data$group_name == 'soc_rsk' | big_data$group_name == 'ind_rsk'])
test <- wilcox.test(big_data$risk[big_data$group_name == 'soc_rsk' | big_data$group_name == 'ind_rsk'],big_data$risk[big_data$group_name == 'soc_amb' | big_data$group_name == 'ind_amb'])
  test$p.value
  Zstat<-qnorm(test$p.value)
  Zstat
  r <- abs(Zstat)/sqrt(N)
  r
  c(Zstat,test$p.value,r)
  median((big_data$risk[big_data$group_name == 'soc_rsk' | big_data$group_name == 'ind_rsk']),na.rm = TRUE)
   median((big_data$risk[big_data$group_name == 'soc_amb' | big_data$group_name == 'ind_amb']),na.rm = TRUE)
  #####
```


```{r}
##### individual all vs social all
N <- length(big_data$risk[big_data$group_name == 'soc_rsk' | big_data$group_name == 'soc_amb'])
test <- wilcox.test(big_data$risk[big_data$group_name == 'ind_rsk' | big_data$group_name == 'ind_amb'],big_data$risk[big_data$group_name == 'soc_rsk' | big_data$group_name == 'soc_amb'])
  test$p.value
  Zstat<-qnorm(test$p.value)
  Zstat
  r <- abs(Zstat)/sqrt(N)
  r
  c(Zstat,test$p.value,r)
median((big_data$risk[big_data$group_name == 'soc_rsk' | big_data$group_name == 'soc_amb']),na.rm = TRUE)
   median((big_data$risk[big_data$group_name == 'ind_rsk' | big_data$group_name == 'ind_amb']),na.rm = TRUE)
```

```{r}
##### individual ambiguity vs individual risky
N <- length(big_data$risk[ big_data$group_name == 'ind_amb'])
test <- wilcox.test(big_data$risk[big_data$group_name == 'ind_rsk'],big_data$risk[big_data$group_name == 'ind_amb' ])
  test$p.value
  Zstat<-qnorm(test$p.value)
  Zstat
  r <- abs(Zstat)/sqrt(N)
  r
  c(Zstat,test$p.value,r)
median(big_data$risk[ big_data$group_name == 'ind_amb'],na.rm = TRUE)
   median(big_data$risk[ big_data$group_name == 'ind_rsk'],na.rm = TRUE)
```

```{r}
##### social ambiguity vs social risky
N <- length(big_data$risk[ big_data$group_name == 'soc_amb'])
test <- wilcox.test(big_data$risk[big_data$group_name == 'soc_rsk'],big_data$risk[big_data$group_name == 'soc_amb' ])
  test$p.value
  Zstat<-qnorm(test$p.value)
  Zstat
  r <- abs(Zstat)/sqrt(N)
  r
  c(Zstat,test$p.value,r)
median(big_data$risk[ big_data$group_name == 'soc_amb'],na.rm = TRUE)
   median(big_data$risk[ big_data$group_name == 'soc_rsk'],na.rm = TRUE)
```

## plot outcome risk_taking
```{r}
library('ggpubr')
library(tidyverse)
library(lme4)

#####
#ind_amb_plot <- ggplot(data=big_ind_amb, aes(risk)) + 
#  geom_histogram(breaks=seq(1, 4, by=.3)) + labs( x="ind_amb choice", y="count")+ geom_text(stat = 'count', aes(label = stat(count)),vjust=-0.1,size=2)  

# ind_amb_plot <- ggplot(data=big_ind_amb, aes(risk)) + 
#           geom_bar(aes(y = (..count..)/sum(..count..))) + 
#           scale_y_continuous(labels=scales::percent) +
#   ylab("relative frequencies") 
# 
# ind_amb_plot
# 
# ind_rsk_plot <- ggplot(data=big_ind_rsk, aes(risk)) + 
#           geom_bar(aes(y = (..count..)/sum(..count..))) + 
#           scale_y_continuous(labels=scales::percent) +
#   ylab("relative frequencies") 
# 
# ind_rsk_plot
# 
# soc_amb_plot <- ggplot(data=big_soc_amb, aes(risk)) + 
#           geom_bar(aes(y = (..count..)/sum(..count..))) + 
#           scale_y_continuous(labels=scales::percent) +
#   ylab("relative frequencies") 
# 
# soc_amb_plot 
# 
# soc_rsk_plot <- ggplot(data=big_soc_rsk, aes(risk)) + 
#           geom_bar(aes(y = (..count..)/sum(..count..))) + 
#           scale_y_continuous(labels=scales::percent) +
#   ylab("relative frequencies") 
# 
# soc_rsk_plot  
# 
# ggarrange(ind_amb_plot,ind_rsk_plot,soc_amb_plot,soc_rsk_plot + rremove("x.text"), 
#           labels = c("A", "B", "C",'D'),
#           ncol = 2, nrow = 2)
```


```{r}
variable_names <- list(
  "ind_amb" = "Individual Ambiguity" ,
  "ind_rsk" = "Individual Risk" ,
  "soc_amb" = "Social Ambiguity" ,
  "soc_rsk" = "Social Risk"
  )


variable_labeller <- function(variable,value){
  return(variable_names[value])
}



ggplot((big_data), aes(x= risk,  group=group_name)) + 
    geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -.6, size=2) +
    labs(y = "Percentage", fill='risk') +
    facet_grid(~group_name,labeller=variable_labeller) +
    scale_y_continuous(labels = scales::percent)+theme_minimal()

```

#person click
```{r}

#to report result of wilcoxin test use this part
N <- length(big_data$person_click[big_data$group_name=='soc_rsk'])
test <- wilcox.test(big_data$person_click[big_data$group_name=='soc_rsk'],big_data$person_click[big_data$group_name=='soc_amb'])
  
  test$p.value
  Zstat<-qnorm(test$p.value)
  Zstat
  r <- abs(Zstat)/sqrt(N)
  r
  c(Zstat,test$p.value,r)
```

# doesnt show number of zeros
```{r}


big_soc <- dplyr::bind_rows(big_soc_rsk,big_soc_amb)
#           ncol = 2, nrow = 2)

variable1_names <- list(

  "soc_amb" = "Social Ambiguity" ,
  "soc_rsk" = "Social Risk"
  )


variable_labeller1 <- function(variable,value){
  return(variable1_names[value])
}

ggplot((big_soc), aes(x= person_click,  group=group_name)) + 
    # with colors geom_bar(aes(y = ..prop.., fill = factor(..x..)), stat="count") +
  # without colors
  geom_bar(aes(y = ..prop..), stat="count") +
    geom_text(aes( label = scales::percent(..prop..),
                   y= ..prop.. ), stat= "count", vjust = -.6, size=2) +
    labs(x='Number of interactions',y = "Percentage", fill='Clicks') +
    facet_grid(~group_name,labeller=variable_labeller1) +
    scale_y_continuous(labels = scales::percent)+theme_minimal()

socdata<- subset(big_data, group_name3=='Social')
inddata<- subset(big_data, group_name3=='Individual')

smodel2<-lmer(person_click~(group_name2)+(1|id)+zother_max_score+zround_score+(1|zfinancial),data = socdata,REML = TRUE)

smodel2r<-lmer(person_click~(1|id)+zother_max_score+zround_score+(1|zfinancial),data = socdata,REML = TRUE)
tab_model(smodel2,smodel2r)


#####
#soc_amb_pplot <- ggplot(data=big_soc_amb, aes(person_click)) + 
  #geom_histogram(breaks=seq(1, 4, by=.3)) + labs( x="soc_amb person click", y="count")+ geom_text(stat = 'count', aes(label = stat(count)),vjust=-0.1,size=2)  
  #soc_amb_pplot 
#soc_rsk_pplot <- ggplot(data=big_soc_rsk, aes(person_click)) + 
 # geom_histogram(breaks=seq(1, 4, by=.3)) + labs( x="soc_rsk person click", y="count")+ geom_text(stat = 'count', aes(label = stat(count)),vjust=-0.1,size=2)  
  # soc_rsk_pplot             


#endplot<-ggarrange(soc_amb_pplot ,soc_rsk_pplot  + rremove("x.text"), 
 #         labels = c("A", "B"),
  #        ncol = 2, nrow = 1)
#endplot                       
```
```{r}
# higher or lower risk-taking and number of clicks relation
# by considering number of zeros

#big_data$person_click[big_data$group_name=='soc_rsk' & is.na(big_data$person_click)] <- 0
#big_data$person_click[big_data$group_name=='soc_amb' & is.na(big_data$person_click)] <- 0
```


```{r}
#####
# check difference between number of clicks in high and low risk taking
N <- length(big_data$person_click[big_data$group_name=='soc_amb'& big_data$risk==1 | big_data$group_name=='soc_rsk'& big_data$risk==1])
test <- wilcox.test(big_data$person_click[big_data$group_name=='soc_amb'& big_data$risk==1 | big_data$group_name=='soc_rsk'& big_data$risk==1],big_data$person_click[big_data$group_name=='soc_amb'& big_data$risk==4 | big_data$group_name=='soc_rsk'& big_data$risk==4])

  test$p.value
  Zstat<-qnorm(test$p.value)
  Zstat
  r <- abs(Zstat)/sqrt(N)
  r
  c(Zstat,test$p.value,r)
  
  #####
```

```{r}
#### difference between risk taking of whom not click vs click 
N <- length(big_data$risk[is.na(big_data$person_click & (big_data$group_name=='soc_risk' | big_data$group_name=='soc_amb'))])
test <- wilcox.test(big_data$risk[is.na(big_data$person_click & (big_data$group_name=='soc_risk' | big_data$group_name=='soc_amb'))],big_data$risk[big_data$person_click==4|big_data$person_click==3|big_data$person_click==2|big_data$person_click==1])

  test$p.value
  Zstat<-qnorm(test$p.value)
  Zstat
  r <- abs(Zstat)/sqrt(N)
  r
  c(Zstat,test$p.value,r)
  median(big_data$risk[is.na(big_data$person_click & (big_data$group_name=='soc_risk' | big_data$group_name=='soc_amb'))],na.rm = TRUE)
  
```


```{r} 
# difference in risk taking of whom do not click in risk and ambiguity groups
N <- length((big_data$risk[is.na(big_data$person_click) & (big_data$group_name=='soc_rsk') ]))
test <- wilcox.test((big_data$risk[is.na(big_data$person_click) & (big_data$group_name=='soc_rsk') ]),(big_data$risk[is.na(big_data$person_click) & (big_data$group_name=='soc_amb') ]))

test$p.value
  Zstat<-qnorm(test$p.value)
  Zstat
  r <- abs(Zstat)/sqrt(N)
  r
  c(Zstat,test$p.value,r)
  median((big_data$risk[is.na(big_data$person_click) & (big_data$group_name=='soc_rsk') ]),na.rm = TRUE)
  
  median((big_data$risk[is.na(big_data$person_click) & (big_data$group_name=='soc_amb') ]),na.rm = TRUE)
```
```{r}
#### difference between risk taking of whom click in risk and ambiguity 
N <- length(big_data$risk[ (big_data$group_name=='soc_rsk') & (big_data$person_click==4|big_data$person_click==3|big_data$person_click==2|big_data$person_click==1) ])

test <- wilcox.test((big_data$risk[ (big_data$group_name=='soc_rsk') & (big_data$person_click==4|big_data$person_click==3|big_data$person_click==2|big_data$person_click==1) ]),(big_data$risk[ (big_data$group_name=='soc_amb') & (big_data$person_click==4|big_data$person_click==3|big_data$person_click==2|big_data$person_click==1) ]))

  test$p.value
  Zstat<-qnorm(test$p.value)
  Zstat
  r <- abs(Zstat)/sqrt(N)
  r
  c(Zstat,test$p.value,r)
  median((big_data$risk[ (big_data$group_name=='soc_rsk') & (big_data$person_click==4|big_data$person_click==3|big_data$person_click==2|big_data$person_click==1) ]),na.rm = TRUE)
  
  median((big_data$risk[ (big_data$group_name=='soc_amb') & (big_data$person_click==4|big_data$person_click==3|big_data$person_click==2|big_data$person_click==1) ]),na.rm = TRUE)
  
```



```{r}#
library(data.table)
#change the order of risk now higher risk is 4 and lower risk is 1
 big_data$risk[big_data$risk==1] <- 5
 big_data$risk[big_data$risk==4] <- 1
 big_data$risk[big_data$risk==5] <- 4
 big_data$risk[big_data$risk==2] <- 5
 big_data$risk[big_data$risk==3] <- 2
 big_data$risk[big_data$risk==5] <- 3
 
 #change values of risk and score to z-score
 big_data$zrisk <- (big_data$risk - mean(big_data$risk,na.rm = TRUE))/sd(big_data$risk,na.rm = TRUE)
 
 big_data$zscore <- (big_data$round_score - mean(big_data$round_score,na.rm = TRUE))/sd(big_data$round_score,na.rm = TRUE)
 
 big_data$zpclick <- (big_data$person_click - mean(big_data$person_click,na.rm = TRUE))/sd(big_data$person_click,na.rm = TRUE)
 # relation between score was taken and next round risk or click
 cor.test(shift(big_data$zscore),(big_data$zrisk))
cor.test(shift(big_data$zscore[big_data$group_name=='soc_amb']),(big_data$zrisk[big_data$group_name=='soc_amb']))

 cor.test(shift(big_data$zscore[big_data$group_name=='soc_rsk']),(big_data$zrisk[big_data$group_name=='soc_rsk']))
 
 cor.test(shift(big_data$zscore[big_data$group_name=='ind_rsk']),(big_data$zrisk[big_data$group_name=='ind_rsk']))
 
 cor.test(shift(big_data$zscore[big_data$group_name=='ind_amb']),(big_data$zrisk[big_data$group_name=='ind_amb']))
 
 cor.test(shift(big_data$zscore),(big_data$zpclick))
 cor.test(shift(big_data$zscore[big_data$group_name=='soc_amb']),(big_data$zpclick[big_data$group_name=='soc_amb']))
 cor.test(shift(big_data$zscore[big_data$group_name=='soc_rsk']),(big_data$zpclick[big_data$group_name=='soc_rsk']))
 
```

```{r}
# test average score taken in each round and next round risk taking to see if its affect risk-taking in social and individual or not
big_data$zominscore <- (big_data$other_min_score - mean(big_data$other_min_score,na.rm = TRUE))/sd(big_data$other_min_score,na.rm = TRUE)

big_data$zomaxscore <- (big_data$other_max_score - mean(big_data$other_max_score,na.rm = TRUE))/sd(big_data$other_max_score,na.rm = TRUE)

big_data$zomeanscore <- (big_data$other_mean_score - mean(big_data$other_mean_score,na.rm = TRUE))/sd(big_data$other_mean_score,na.rm = TRUE)

cor.test(shift(big_data$zrisk,-1),big_data$zomeanscore)
cor.test(shift(big_data$zrisk,-1),big_data$zomaxscore)
cor.test(shift(big_data$zrisk,-1),big_data$zominscore)
cor.test(shift(big_data$zrisk[big_data$group_name=='soc_amb'],-1),big_data$zomeanscore[big_data$group_name=='soc_amb'])
cor.test(shift(big_data$zrisk[big_data$group_name=='soc_amb'],-1),big_data$zomaxscore[big_data$group_name=='soc_amb'])
cor.test(shift(big_data$zrisk[big_data$group_name=='soc_amb'],-1),big_data$zominscore[big_data$group_name=='soc_amb'])

cor.test(shift(big_data$zrisk[big_data$group_name=='soc_rsk'],-1),big_data$zomeanscore[big_data$group_name=='soc_rsk'])
cor.test(shift(big_data$zrisk[big_data$group_name=='soc_rsk'],-1),big_data$zomaxscore[big_data$group_name=='soc_rsk'])
cor.test(shift(big_data$zrisk[big_data$group_name=='soc_rsk'],-1),big_data$zominscore[big_data$group_name=='soc_rsk'])

# mean score
cor.test(shift(big_data$zrisk[big_data$group_name=='soc_rsk'|big_data$group_name=='soc_amb'],-1),(big_data$zomeanscore[big_data$group_name=='soc_rsk'|big_data$group_name=='soc_amb'] - big_data$zscore[big_data$group_name=='soc_rsk'|big_data$group_name=='soc_amb']))


cor.test(shift(big_data$zrisk[big_data$group_name=='soc_amb'],-1),(big_data$zomeanscore[big_data$group_name=='soc_amb'] - big_data$zscore[big_data$group_name=='soc_amb']))

cor.test(shift(big_data$zrisk[big_data$group_name=='soc_rsk'],-1),(big_data$zomeanscore[big_data$group_name=='soc_rsk'] - big_data$zscore[big_data$group_name=='soc_rsk']))


#max score

cor.test(shift(big_data$zrisk[big_data$group_name=='soc_rsk'|big_data$group_name=='soc_amb'],-1),(big_data$zomaxscore[big_data$group_name=='soc_rsk'|big_data$group_name=='soc_amb'] - big_data$zscore[big_data$group_name=='soc_rsk'|big_data$group_name=='soc_amb']))

cor.test(shift(big_data$zrisk[big_data$group_name=='soc_amb'],-1),(big_data$zomaxscore[big_data$group_name=='soc_amb'] - big_data$zscore[big_data$group_name=='soc_amb']))

cor.test(shift(big_data$zrisk[big_data$group_name=='soc_rsk'],-1),(big_data$zomaxscore[big_data$group_name=='soc_rsk'] - big_data$zscore[big_data$group_name=='soc_rsk']))


#min score

cor.test(shift(big_data$zrisk[big_data$group_name=='soc_rsk'|big_data$group_name=='soc_amb'],-1),(big_data$zominscore[big_data$group_name=='soc_rsk'|big_data$group_name=='soc_amb'] - big_data$zscore[big_data$group_name=='soc_rsk'|big_data$group_name=='soc_amb']))

cor.test(shift(big_data$zrisk[big_data$group_name=='soc_amb'],-1),(big_data$zominscore[big_data$group_name=='soc_amb'] - big_data$zscore[big_data$group_name=='soc_amb']))

cor.test(shift(big_data$zrisk[big_data$group_name=='soc_rsk'],-1),(big_data$zominscore[big_data$group_name=='soc_rsk'] - big_data$zscore[big_data$group_name=='soc_rsk']))
#remove NA from dospert
#big_data<-big_data[-which(is.na(big_data$dospert)),]

```



```{r}
#for probability of taken risk
big_data$risklabel<-big_data$risk
 big_data$risklabel[big_data$risklabel==1] <- 5
 big_data$risklabel[big_data$risklabel==4] <- 1
 big_data$risklabel[big_data$risklabel==5] <- 4
 big_data$risklabel[big_data$risklabel==2] <- 5
 big_data$risklabel[big_data$risklabel==3] <- 2
 big_data$risklabel[big_data$risklabel==5] <- 3
big_data$loseprobability<-1-(big_data$probability)
   big_data$expectation<-(abs(big_data$round_score)*big_data$probability)-(abs(big_data$round_score)*big_data$loseprobability)
# big_data$zprobrisk <- scale(big_data$probrisk)
ggplot(big_data, aes(x=expectation, fill=group_name, color=group_name)) 
+     geom_histogram(position="identity", alpha=0.5)+facet_grid(group_name ~ .)

ggplot(big_data, aes(x=zprobrisk, group=group_name)) +
    geom_histogram(position="identity", alpha=0.5)+facet_grid(~group_name,labeller=variable_labeller)+labs(x="Probability of choice", y = "Count")
model1<-lmer(zprobrisk~group_name+(1|id),data = big_data,REML = FALSE)
model1r<-lmer(zprobrisk~(1|id),data = big_data,REML = FALSE)
anova(model1,model1r)
model2<-lmer(zprobrisk~group_name+(1|id),data = big_data,REML = FALSE)

smodel<-lmer(zrisk~group_name2+(1|id)+zround_score+zfinancial+gender+zother_max_score+zother_min_score,data = socdata,REML = TRUE)

imodel<-lmer(zrisk~group_name2+(1|id)+zround_score+zfinancial+gender,data = inddata,REML = TRUE)

bmodel<-lmer(zrisk~group_name2+(1|id)+zround_score+zfinancial+gender,data = big_data,REML = TRUE)


ggplot((big_data), aes(x= risklabel,  group=group_name)) + 
    geom_histogram(position="identity", alpha=0.5) +

    labs(y = "Count",x='risk label', fill='risklabel') +
    #facet_grid(group_name2~group_name3,labeller=variable_labeller) +
    facet_grid(group_name2~group_name3) +theme_minimal()

ggplot((big_data), aes(x= winprobrisk,  group=group_name)) + 
    geom_histogram(position="identity", alpha=0.5) +

    labs(y = "Count",x='winning probability', fill='winprobrisk') +
    #facet_grid(group_name2~group_name3,labeller=variable_labeller) +
    facet_grid(group_name2~group_name3) +theme_minimal()


ggplot((big_data), aes(x= expectation,  group=group_name)) + 
    geom_histogram(position="identity", alpha=0.5) +

    labs(y = "Count", fill='expectation') +
    #facet_grid(group_name2~group_name3,labeller=variable_labeller) +
    facet_grid(group_name2~group_name3) +theme_minimal()

ggplot(socdata, aes(x=person_click, group=group_name)) +
    geom_histogram(position="identity", alpha=0.5)+facet_grid(~group_name,labeller=variable_labeller)+labs(x="click on others", y = "Count")+theme_minimal()

```




```{r}
model3<-lmer(scale((expectation))~(group_name2:scale(other_min_score))+(group_name2:scale(other_max_score))+(group_name2:scale(person_click))+(scale(other_min_score):person_click)+(scale(other_min_score):person_click)+(1|id),data = socdata,REML = FALSE)

stargazer(model3, type = "text",
          digits = 3,
          star.cutoffs = c(0.05, 0.01, 0.001),
          digit.separator = "")
model3<-lmer(scale((other_min_score))~(group_name2)+(1|id),data = socdata,REML = FALSE)
model1<-lmer(scale((expectation))~scale(other_max_score)+scale(other_min_score)+(1|id),data = socdata,REML = FALSE)
model1<-lmer(scale((person_click))~scale(other_max_score)+scale(other_min_score)+(1|id),data = socdata,REML = FALSE)
```


##checked and work properly

```{r}
#####
tmpscore <- array(NA,5)
tmprisk <- array(NA,5)
avg_soc_amb_score <- array(NA,50)
avg_soc_amb_risk <- array(NA,50)
for (j in 1:50){
for (i in 1:5){
  tmpscore[i] <- (
big_soc_amb$round_score[big_soc_amb$round_number == j & big_soc_amb$participant_number ==i])
  
tmprisk[i] <- (
big_soc_amb$risk[big_soc_amb$round_number == j & big_soc_amb$participant_number ==i])
}
avg_soc_amb_score[j]<- median(tmpscore)
avg_soc_amb_risk[j]<- median(tmprisk)
}

cor.test((avg_soc_amb_risk - mean(avg_soc_amb_risk))/sd(avg_soc_amb_risk),(avg_soc_amb_score - mean(avg_soc_amb_score))/sd(avg_soc_amb_score))
```







```{r}
#####

 

soc_amb_pplot <- ggplot(data=big_person_soc_amb, aes(person_click)) + 
  geom_histogram() + labs( x="number of social selection in ambiguity", y="count")+ geom_text(stat = 'count', aes(label = stat(count)),vjust=-0.1,size=2)  

soc_rsk_pplot <- ggplot(data=big_person_soc_rsk, aes(person_click)) + 
  geom_histogram() + labs( x="number of social selection in risky", y="count")+ geom_text(stat = 'count', aes(label = stat(count)),vjust=-0.1,size=2)

ggarrange(soc_amb_pplot,soc_rsk_pplot + rremove("x.text"), 
          labels = c("A", "B"),
          ncol = 2)

```

Plots shows difference in the distribution of choices in social ambiguity.A shows individual ambiguity, B shows individual risky, C shows social ambiguity and  ind_amb_plotsoc_amb_plot,soc_rs
```{r}
#####
#plot based on group choice
library(ggplot2)

# Notched box plot
ggplot(big_data, aes(x=group_name, y=risk)) + 
  geom_boxplot(notch=TRUE)+ labs(title="plot of choice risk by all groups", x="groups", y="choice number")
#####
#test for normality
#install.packages("dplyr")
#if(!require(devtools)) install.packages("devtools")
#devtools::install_github("kassambara/ggpubr")
library("dplyr")
library("ggpubr")
library(ggpubr)
shapiro.test(big_data$risk)
# data is not normally distributed
#it is significant thus data is not normal
# https://www.datanovia.com/en/lessons/normality-test-in-r/
# so hypothesis should be tested using non-parametric tests.
##### 
#analysis
```





## changes by time - trial by trial
```{r}
round_ind_amb <- array(0,50)
for (i in round_number){
  round_ind_amb[i] <-mean( big_ind_amb$risk[big_ind_amb$round_number ==i], na.rm = TRUE)
}

  plot(round_ind_amb,main="mean of selected options in individual_ambiguity ", 
      xlab="round",ylab = 'mean',type = 'l')
  
  round_ind_rsk <- array(0,50)
for (i in round_number){
  round_ind_rsk[i] <-mean( big_ind_rsk$risk[big_ind_rsk$round_number ==i], na.rm = TRUE)
}
 
   plot(round_ind_rsk,main="mean of selected options in individual_risky ", 
      xlab="round",ylab = 'mean',type = 'l')
  
  round_soc_amb <- array(0,50)
for (i in round_number){
  round_soc_amb[i] <-mean( big_soc_amb$risk[big_soc_amb$round_number ==i])
}
 
   plot(round_soc_amb,main="mean of selected options in social_ambiguity ", 
      xlab="round",ylab = 'mean',type = 'l')
  
    round_soc_rsk <- array(0,50)
for (i in round_number){
  round_soc_rsk[i] <-mean( big_soc_rsk$risk[big_soc_rsk$round_number ==i])
}
    plot(round_soc_rsk,main="mean of selected options in social_risky ", 
      xlab="round",ylab = 'mean',type = 'l')
```


#### Social part
```{r}
soc_rsk_person <- array(NA, dim=c(length(participant_data_soc_rsk),50,5))
for (i in 1:length(participant_data_soc_rsk))
{
  player_number_game_data_soc_rsk[i] <- game_data_soc_rsk[[i]][["maxPlayers"]]
}
for (i in 1:length(participant_data_soc_rsk))# loop over group of participants play at the same time1
{ 
  for (j in 1:50) # loop over rounds
  {
    for (k in 1:5 ) #loop over number of participants in each test
    { 
      if ((k >player_number_game_data_soc_rsk[i])) 
      {
        soc_rsk_person[i,j,k] <- NA
      }
      else{
        if (length(game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["socialSceneData"]]) != 0){
          soc_rsk_person[i,j,k] <- (length(game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["socialSceneData"]][[1]][["selectedParticipantId"]]))
        }
      }
    }
  }
}


soc_amb_person <- array(NA, dim=c(length(participant_data_soc_amb),50,5))
for (i in 1:length(participant_data_soc_amb))
{
  player_number_game_data_soc_amb[i] <- game_data_soc_amb[[i]][["maxPlayers"]]
}
for (i in 1:length(participant_data_soc_amb))# loop over group of participants play at the same time1
{ 
  for (j in 1:50) # loop over rounds
  {
    for (k in 1:5 ) #loop over number of participants in each test
    { 
      if ((k >player_number_game_data_soc_amb[i])) 
      {
        soc_amb_person[i,j,k] <- NA
      }
      else{
        if (length(game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["socialSceneData"]]) != 0){
          soc_amb_person[i,j,k] <- (length(game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["socialSceneData"]][[1]][["selectedParticipantId"]]))
        #  soc_amb_other_scores[i,j,k]
        }
      }
    }
  }
}



#soc_amb
participant_number <-1
group_name <- 'soc_amb'
tmplist <- list()

for (i in 1:length(participant_data_soc_amb)){
  datalist <- list()
  for (k in 1:player_number_game_data_soc_amb[i]) # participants
  {
    personclk <- array(0,50)
    round_number <- 1:50
    personclk <- soc_amb_person[i,round_number,k]
    risk <- soc_amb_choice[i,round_number,k]
        if (risk == 4){
      probab<-prob$prob1[round_number]
    }else if (risk == 3){
      probab<-prob$prob2[round_number]
    }else if (risk == 2){
      probab<-prob$prob3[round_number]
    }else if (risk == 1){
      probab<-prob$prob4[round_number]
    }
    d <- (data.frame('participant_number'= participant_number,'group_name'= group_name,'round_number'= round_number,'person_click'= personclk,'risk'=risk,'probability'=probab,'data_gathering_group'=i,'data_gathering_participant_id'= k))
    datalist[[k]] <- d
    participant_number <- participant_number + 1
  }
  tmplist[[i]] <- dplyr::bind_rows(datalist)
}
big_person_soc_amb <- dplyr::bind_rows(tmplist)
big_person_soc_amb$person_click[round_number == 50] <- 0

##########
```


```{r}
#####
## social risk choice counting
player_number_game_data_soc_rsk <- NULL
tmprounddata <- NULL
soc_rsk_choice <- array(NA, dim=c(5,50,5))
soc_rsk_score <- array(NA, dim=c(5,50,5))
participant_id_soc_rsk <- array(NA, dim=c(5,50,5)) 
rounddata <- NULL
testdata <- NULL
choice_number <- NULL

for (i in 1:length(participant_data_soc_rsk))
{
  player_number_game_data_soc_rsk[i] <- game_data_soc_rsk[[i]][["maxPlayers"]]
}
#group of participants
for (i in 1:length(participant_data_soc_rsk))# loop over group of participants play at the same time1
{ 
  for (j in 1:50) # loop over rounds
  {
    for (k in 1:5 ) #loop over number of participants in each test
    { 
      if ((k >player_number_game_data_soc_rsk[i])) 
      {
        soc_rsk_choice[i,j,k] <- NA
        soc_rsk_score[i,j,k] <- NA
      }
      else{
        if (length(game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]]) != 0){
          soc_rsk_choice[i,j,k] <- (length(game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["selectedColors"]]))
          soc_rsk_score[i,j,k] <-( game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["result"]])           participant_id_soc_rsk[i,j,k] <- game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["clientId"]]
        }
      }
      
    }
  }
}
######
```


```{r}
######
#soc_rsk
participant_number <-1
group_name <- 'soc_rsk'
tmplist <- list()

for (i in 1:length(participant_data_soc_rsk)){
  datalist <- list()
  for (k in 1:player_number_game_data_soc_rsk[i]) # participants
  {
    personclk <- array(0,50)
    round_number <- 1:50
    trialscore<-soc_rsk_score[i,round_number,k]
    personclk <- soc_rsk_person[i,round_number,k]
    risk <- soc_rsk_choice[i,round_number,k]
        if (risk == 4){
      probab<-prob$prob1[round_number]
    }else if (risk == 3){
      probab<-prob$prob2[round_number]
    }else if (risk == 2){
      probab<-prob$prob3[round_number]
    }else if (risk == 1){
      probab<-prob$prob4[round_number]
    }
    id <- participant_id_soc_rsk[i,round_number,k]
    d <- (data.frame('participant_number'= participant_number,'id'=id,'group_name'= group_name,'round_number'= round_number,'round_score'=trialscore,'person_click'= personclk,'risk'=risk,'probability'=probab,'data_gathering_group'=i,'data_gathering_participant_id'= k))
    datalist[[k]] <- d
    participant_number <- participant_number + 1
  }
  tmplist[[i]] <- dplyr::bind_rows(datalist)
}
big_person_soc_rsk <- dplyr::bind_rows(tmplist)
big_person_soc_rsk$person_click[round_number == 50] <- 0
#big_person <-  dplyr::bind_rows(big_person_soc_rsk,big_person_soc_amb)
```

```{r}


ggplot(big_person, aes(x=group_name, y=person_click)) + 
  geom_boxplot(notch=TRUE) +  ggtitle("Number of selected person by risk and ambiguity groups") +
  xlab("group") + ylab("number of selected person")

person_res_ra <- wilcox.test(person_click ~ group_name, data = big_person,  exact = FALSE)
person_res_ra

ggplot(data=big_person_soc_amb, aes(person_click)) + 
  geom_histogram() + labs(title="Histogram for person clicks in social_ambiguity", x="number of person click", y="count")+ geom_text(stat = 'count', aes(label = stat(count), vjust = -0.2)) 

ggplot(data=big_person_soc_rsk, aes(person_click)) + 
  geom_histogram() + labs(title="Histogram for person clicks in social_risky", x="number of person click", y="count") + geom_text(stat = 'count', aes(label = stat(count), vjust = -0.2)) 

round_person_soc_amb <- array(0,50)
for (i in round_number){
  round_person_soc_amb[i] <-mean( big_person_soc_amb$person_click[big_person_soc_amb$round_number ==i])
}

plot(round_person_soc_amb,main="mean of selected person in social_ambiguity ", 
     xlab="round",ylab = 'mean',type = 'l')

round_person_soc_rsk <- array(0,50)
for (i in round_number){
  round_person_soc_rsk[i] <-mean( big_person_soc_rsk$person_click[big_person_soc_rsk$round_number ==i])
}

plot(round_person_soc_rsk,main="mean of selected person in social_risky ", 
     xlab="round",ylab = 'mean',type = 'l')



```
The difference between risk and ambiguity is significant by p_value `r person_res_ra$p.value`. In social ambiguity they click more on the other people.
Trial by trial plot shows a decrease in the number of click on the other people in risky situation from the beginning. 

```{r}
# check whether click on others leads more risk-taking or not
cor.test(big_person_soc_amb$person_click[big_person_soc_amb$person_click != 0],big_person_soc_amb$risk[big_person_soc_amb$person_click != 0])

cor.test(big_person_soc_rsk$person_click[big_person_soc_rsk$person_click != 0],big_person_soc_rsk$risk[big_person_soc_rsk$person_click != 0])
#no click histogram
hist(big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 0])
#one click histogram
hist(big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 1])
#two click histogram
hist(big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 2])
#three click histogram
hist(big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 3])
#four click histogram
hist(big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 4])

#no click histogram
hist(big_person_soc_amb$risk[big_person_soc_amb$person_click == 0])
#one click histogram
hist(big_person_soc_amb$risk[big_person_soc_amb$person_click == 1])
#two click histogram
hist(big_person_soc_amb$risk[big_person_soc_amb$person_click == 2])
#three click histogram
hist(big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 3])
#four click histogram
hist(big_person_soc_rsk$risk[big_person_soc_amb$person_click == 4])


wilcox.test(big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 4],big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 0])

wilcox.test(big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 4],big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 1])

wilcox.test(big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 4],big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 2])

wilcox.test(big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 4],big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 3])

wilcox.test(big_person_soc_amb$risk[big_person_soc_amb$person_click == 4],big_person_soc_amb$risk[big_person_soc_amb$person_click == 0])

wilcox.test(big_person_soc_amb$risk[big_person_soc_amb$person_click == 1],big_person_soc_amb$risk[big_person_soc_amb$person_click == 4],alternative = 'greater')
```
Results show significant negative correlation between number of click and risk-taking in the social ambiguity condition but not in the social risk condition. It shows people who click on the others take less risk than the others in ambiguity condition. 

```{r}
wilcox.test(big_person_soc_rsk$risk[big_person_soc_rsk$person_click],big_person_soc_amb$risk[big_person_soc_amb$person_click])

wilcox.test(big_person_soc_amb$risk[big_person_soc_amb$person_click == 0 || big_person_soc_amb$person_click == 1 || big_person_soc_amb$person_click == 2 || big_person_soc_amb$person_click == 3 || big_person_soc_amb$person_click == 4],big_person_soc_rsk$risk[big_person_soc_rsk$person_click == 0 || big_person_soc_rsk$person_click == 1 || big_person_soc_rsk$person_click == 2 || big_person_soc_rsk$person_click == 3 || big_person_soc_rsk$person_click == 4])

wilcox.test(big_person_soc_amb$risk[big_person_soc_amb$person_click ==3],big_person_soc_amb$risk[big_person_soc_amb$person_click ==4])

wilcox.test(big_person_soc_rsk$risk[big_person_soc_rsk$person_click ==4],big_person_soc_amb$risk[big_person_soc_amb$person_click ==4])

chrsk_amb_clk4 <- big_person_soc_amb$risk[big_person_soc_amb$person_click ==4]
chrsk_amb_clk3 <- big_person_soc_amb$risk[big_person_soc_amb$person_click ==3]
chrsk_amb_clk2 <- big_person_soc_amb$risk[big_person_soc_amb$person_click ==2]
chrsk_amb_clk1 <- big_person_soc_amb$risk[big_person_soc_amb$person_click ==1]
chrsk_amb_clk0 <- big_person_soc_amb$risk[big_person_soc_amb$person_click ==0]

chrsk_rsk_clk4 <- big_person_soc_rak$risk[big_person_soc_rsk$person_click ==4]
chrsk_rsk_clk3 <- big_person_soc_rsk$risk[big_person_soc_rsk$person_click ==3]
chrsk_rsk_clk2 <- big_person_soc_rsk$risk[big_person_soc_rsk$person_click ==2]
chrsk_rsk_clk1 <- big_person_soc_rsk$risk[big_person_soc_rsk$person_click ==1]
chrsk_rsk_clk0 <- big_person_soc_rsk$risk[big_person_soc_rsk$person_click ==0]
boxplot(chrsk_rsk_clk4,chrsk_rsk_clk3,chrsk_rsk_clk2,chrsk_rsk_clk1,chrsk_rsk_clk0,chrsk_amb_clk4,chrsk_amb_clk3,chrsk_amb_clk2,chrsk_amb_clk1,chrsk_amb_clk0)
ch_click_data <- data.frame()
boxplot(big_person_soc_rsk$risk[big_person_soc_rsk$person_click ==4],big_person_soc_amb$risk[big_person_soc_amb$person_click ==4])


client_id_soc_rsk <- NA
client_id_soc_amb <- NA
for (i in 1:5){
 client_id_soc_rsk[i] <- game_data_soc_rsk[[1]][["roundData"]][[1]][["participantRoundData"]][[i]][["clientId"]]
 client_id_soc_amb[i] <- game_data_soc_amb[[1]][["roundData"]][[1]][["participantRoundData"]][[i]][["clientId"]]
  
}
# giving index of id
round_score_rsk <- array(NA,c(5,50,5))
for (i in 1:5){ # group at the time of running
  for (j in 1:50) {# rounds
    for(k in 1:5){#participants
       round_score_rsk[i,j,k] <- game_data_soc_rsk[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["result"]] 
    }
  }
}
match('0GQP9v-YC',client_id_soc_amb)


```
```{r}
chrsk_amb_clk4 <- big_person_soc_amb$risk[big_person_soc_amb$person_click ==4]
chrsk_amb_clk3 <- big_person_soc_amb$risk[big_person_soc_amb$person_click ==3]
chrsk_amb_clk2 <- big_person_soc_amb$risk[big_person_soc_amb$person_click ==2]
chrsk_amb_clk1 <- big_person_soc_amb$risk[big_person_soc_amb$person_click ==1]
chrsk_amb_clk0 <- big_person_soc_amb$risk[big_person_soc_amb$person_click ==0]

chrsk_rsk_clk4 <- big_person_soc_rsk$risk[big_person_soc_rsk$person_click ==4]
chrsk_rsk_clk3 <- big_person_soc_rsk$risk[big_person_soc_rsk$person_click ==3]
chrsk_rsk_clk2 <- big_person_soc_rsk$risk[big_person_soc_rsk$person_click ==2]
chrsk_rsk_clk1 <- big_person_soc_rsk$risk[big_person_soc_rsk$person_click ==1]
chrsk_rsk_clk0 <- big_person_soc_rsk$risk[big_person_soc_rsk$person_click ==0]
boxplot(chrsk_rsk_clk0,chrsk_rsk_clk1,chrsk_rsk_clk2,chrsk_rsk_clk3,chrsk_rsk_clk4,chrsk_amb_clk0,chrsk_amb_clk1,chrsk_amb_clk2,chrsk_amb_clk3,chrsk_amb_clk4,ylab ='selected option', xlab =' \n \n risky / ambiguity social click numbers',
        names = c("0", "1", "2", "3",'4',"0", "1", "2", "3",'4'),main = "Risky choice in social ambiguity and social risky groups \n by considering social clicks",at =c(1,2,3,4,5,7,8,9,10, 11))



```
```{r}
#Dospert data
#TO DO
#check remove data
#implement scores
dospert <- read.csv("~/Downloads/Domain-Specific Risk-Taking (Adult) Scale – Risk Taking_October 6, 2020_22.58.csv", header=TRUE)
Dospert <- data.frame(id=dospert$userID,Q1=dospert$Q1,Q2=dospert$Q2,Q3=dospert$Q3,Q4=dospert$Q4,Q5=dospert$Q5,Q6=dospert$Q6,Q7=dospert$Q7,Q8=dospert$Q8,Q9=dospert$Q9,Q10=dospert$Q10,Q11=dospert$Q11,Q12=dospert$Q12,Q13=dospert$Q13,Q14=dospert$Q14,Q15=dospert$Q15,Q16=dospert$Q16,Q17=dospert$Q17,Q18=dospert$Q18,Q19=dospert$Q19,Q20=dospert$Q20,Q21=dospert$Q21,Q22=dospert$Q22,Q23=dospert$Q23,Q24=dospert$Q24,Q25=dospert$Q25,Q26=dospert$Q26,Q27=dospert$Q27,Q28=dospert$Q28,Q29=dospert$Q29,Q30=dospert$Q30)

```

find highest outcome of others in each round or average outcome of others 
check their effect on risk-taking of one person in each round. It is true that they don't click but they see the others outcome without click and it could leads to competition.

```{r}
#####
## social ambiguity choice counting
player_number_game_data_soc_amb <- NULL
tmprounddata <- NULL
soc_amb_choice <- array(NA, dim=c(5,50,5))
soc_amb_score <- array(NA, dim=c(5,50,5))
participant_id_soc_amb <- array(NA, dim=c(5,50,5)) 
rounddata <- NULL
testdata <- NULL
choice_number <- NULL

for (i in 1:length(participant_data_soc_amb))
{
  player_number_game_data_soc_amb[i] <- game_data_soc_amb[[i]][["maxPlayers"]]
}
#group of participants
for (i in 1:length(participant_data_soc_amb))# loop over group of participants play at the same time1
{ 
  for (j in 1:50) # loop over rounds
  {
    for (k in 1:5 ) #loop over number of participants in each test
    { 
      if ((k >player_number_game_data_soc_amb[i])) 
      {
        soc_amb_choice[i,j,k] <- NA
        soc_amb_score[i,j,k] <- NA
      }
      else{
        if (length(game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]]) != 0){
          soc_amb_choice[i,j,k] <- (length(game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["selectedColors"]]))
          soc_amb_score[i,j,k] <-( game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["bubbleSceneData"]][[1]][["result"]])           participant_id_soc_amb[i,j,k] <- game_data_soc_amb[[i]][["roundData"]][[j]][["participantRoundData"]][[k]][["clientId"]]
        }
      }
      
    }
  }
}


soc_amb_data <- data.frame(pid=participant_id_soc_amb,score=soc_amb_score,risk=soc_amb_choice,pclk = soc_amb_person)
```





